\documentclass[a4paper, 12pt]{article}
\begin{document}
\title{Key Engineering Skills}
\date{}
\maketitle

	\section*{Introduction}
		Lecturer: C. Dunnill, office hour is Monday 12pm, but just drop him an email and he should be available whenever. Emails are necessary as he's in ESRI which is card entry only.  \\
		ICT labs are on Monday, not Friday. All lectures are recorded and available on Blackboard. 
	
		\subsection*{Testing}
			All testing is coursework based, there are no exams. There are five major assignments: \begin{itemize}
			\item Oral Presentation (three minute YouTube video)
			\item CV
			\item MATLAB
			\item Graphical Presentation
			\item Project Planning
		\end{itemize}
	
	\section*{Lecture 1: Transitioning to University \hfill \date{05/10/17}}
		Lectures are incredibly busy, so although students are important don't expect an email reply immediately.
		
		\subsection*{During Lectures}
			Turning up is helpful, you will learn much better from a lecture than looking at slides. The emphasis is on us to learn more than for the lecturer to teach us, this is different to school.
			
		\subsection*{Revision Tips}
			\begin{itemize}
				\item Create posters - Get to the point where you can visualise them with eyes closed
				\item Take a lot of break, 45 minutes of work per hour
				\item Be active while revise
				\item Chew gum
				\item Have your short and long term motivation 
				\begin{itemize}
					\item If I finish this assignment I can go out
					\item I need a degree to go into R\&D
				\end{itemize}
				\item Break long term goals down into short term goals
				\item Build up your goals. I will do four blocks of revision today, then 5, then 6 etc. Don't start with your goals too high
				\item Think about failure, why can't you fail?
			\end{itemize}

\end{document}