\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\begin{document}

\title{Society Training}
\maketitle

\newpage

\tableofcontents

\newpage

\section{Volunteering}
	Log hours worked for society at \url{www.swansea-union.co.uk/volunteering}. Keeps track of hours and activities done, so useful for putting on a resume.
	
\section{Handbook}
	There's a handbook on the facebook page. Will cover:
	\begin{itemize}
		\item Room bookings
		\item AGMs
		\item HEAR
		\item Website 
		\item etc. 
	\end{itemize}
	
\section{Travel}
	Can book coaches and Minibusses through them, payments are done through finance. Minibus drivers need to be at least 21 and need 3 years driving experience, as well as a British license. 
	
\section{Equipment Available}
	Can be "rented" for free.
	\begin{itemize}
		\item Charity Box/ Bucket
		\item Go Pro
		\item Camera
		\item Tripod
		\item Microphone
		\item Gazebo
		\item More
	\end{itemize}
	
\section{Disciplinary}
	Route that should be taken is:
	\begin{itemize}
		\item Committee members
		\item Hold a meeting
		\item Talk to Exec
		\item Talk to chris
		\item Disciplinary meeting
		\item Vote of No Confidence
	\end{itemize}		
	Vote of No Confidence is a last resort, and should only be used as such.
	
\section{Freshers Fayre}
	\subsection{Rules}
		\begin{itemize}
			\item All promotianal material in English and Welsh
			\item Set up form 8:30am
			\item Cashless
			\item Half a table
			\item Don't be a dick
			\item No fun (Alcohol or drugs)
			\item No Leafletting
			\item Sponsorships go through Chris or Geri
			\item Tidy up after
		\end{itemize}
		
	\subsection{Tips}
		\begin{itemize}
			\item Tiny table, use a rota
			\item Bring Scissors, extension lead
			\item Have first event planned
			\item Flyers
			\item Use a tablecloth
			\item Have a sign up sheet
			\item It's loud, audio from a laptop won't work
			\item Presentation running on a laptop showing events etc.
			\item Have a disclaimer on sign up sheet saying what we'll use the info for
			\item Colour is good
			\item Photos should be large so they can be seen
		\end{itemize}
			
\section{Crowd Funding}
	Wave is their crowdfunding platform. Can be found at \url{wave.swansea.ac.uk}. Straight up copying the University Of Yorks' funding site, YuStart. 
	\\ Could be useful, even if their presentation was painfully souless.
	
\section{STaRS}
	The Societies Tiers and Reward System \\
	\\
	There are three different tiers; Bronze, Silver and Gold. Bronze has 15 compulsory goals, silver has 10 compulsory and 5 optional goals, and gold has 7 compulsory and 8 optional goals. \\
	\\
	Completing Silver or Gold tiers gets you entered into a raffle for cash and completing gold tier earns Summer Ball VIP tickets. 
	
\section{Room Bookings and Risk Assessments}
	\subsection{The Form}	
		Can be got from \url{www.swansea-union.co.uk/societies}
		
\section{The Website}
	\url{www.swansea-union.co.uk} \\
	When you log in log in as staff. \\ 
	It can be used to send an email to all paid members of the societies.

\section{Finances}
	Accessible via finance cards which are available to the President or Treasurer. \\
	\\
	Sort Code: 30-98-85 \\
	Account Number: 00891532 \\
	Reference should be the Society Name \\
	\\
	When withdrawing you can either withdraw cash, do a bank transfer or pay an invoice. \\
	When withdrawing cash they need the recipt for what was paid. \\
	Any payments less that £200 must be paid in cash, while any larger is done through BACS \\
	Reimbursments must be counter signed by either the President or Treasurer, they can not be counter signed by the same person filing the reimbursment. \\
	Invoices must be sent from the official society email. \\
	There is normally a two day clearing period on any payments made. \\

\end{document}